MINOS Transition Models

### 2022-12-19 docsrc/Coefficients/summarise_transitions_2.tex
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

\begin{verbatim}
## -- Attaching packages ------------------------------------------------------------------------------- tidyverse 1.3.2 --
## v ggplot2 3.3.6      v purrr   0.3.4 
## v tibble  3.1.8      v dplyr   1.0.10
## v tidyr   1.2.0      v stringr 1.4.0 
## v readr   2.1.2      v forcats 0.5.1 
## -- Conflicts ---------------------------------------------------------------------------------- tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

>>>>

\begin{verbatim}
## -- Attaching packages ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- tidyverse 1.3.2 --
## v ggplot2 3.3.6      v purrr   0.3.4 
## v tibble  3.1.8      v dplyr   1.0.10
## v tidyr   1.2.0      v stringr 1.4.0 
## v readr   2.1.2      v forcats 0.5.1 
## -- Conflicts ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

### 2022-12-19 docsrc/documentation/notebooks/summarise_transitions_2.Rmd
automate rendering of R notebooks into sphinx. Rmd references as well using pandoc.

---
title: "MINOS Transition Models"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

@@

```{r}
options(width=120)
require(tidyverse)
require(pscl)

workingDir <- "../.." #TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.
knitr::opts_knit$set(root.dir = workingDir)
trans.path <- paste0(workingDir,'/data/transitions/test/')
tobacco <- readRDS(paste0(trans.path, 'tobacco_zip_2018_2019.rds'))
summary(tobacco)
```

>>>>

---
title: "MINOS Transition Models"
output: html_document
bibliography: 
  - "refs.bib"
---

@@

Test references [@1987:nelson].

@@

```{r tobacco_output}
options(width=120)
require(tidyverse)
require(pscl)

workingDir <- "../../.." #TODO stored in docsrc/Coefficients for now. move to data/transitions and change rst filepaths accordingly.
knitr::opts_knit$set(root.dir = workingDir)
trans.path <- paste0(workingDir,'/data/transitions/test/')
tobacco <- readRDS(paste0(trans.path, 'tobacco_zip_2018_2019.rds'))
summary(tobacco)
```

References
----------
